Strings functions analysis

### 2022-08-29 article.tex
python functions existing added

    \begin{longtable}{lllllllllll}
        \hline
        & \begin{sideways}Java\end{sideways}
        & \begin{sideways}Ruby\end{sideways}
        & \begin{sideways}Python\end{sideways}
        & \begin{sideways}C++\end{sideways}
        & \begin{sideways}JavaScript\end{sideways}
        & \begin{sideways}Go\end{sideways}
        & \begin{sideways}C\#\end{sideways}
        & \begin{sideways}Swift\end{sideways}
        & \begin{sideways}PHP\end{sideways}
        & \begin{sideways}Rust\end{sideways}
        \\
        \hline
        \endfirsthead
        \multicolumn{11}{c}%
        {\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
        \hline
        & \begin{sideways}Java\end{sideways}
        & \begin{sideways}Ruby\end{sideways}
        & \begin{sideways}Python\end{sideways}
        & \begin{sideways}C++\end{sideways}
        & \begin{sideways}JavaScript\end{sideways}
        & \begin{sideways}Go\end{sideways}
        & \begin{sideways}C\#\end{sideways}
        & \begin{sideways}Swift\end{sideways}
        & \begin{sideways}PHP\end{sideways}
        & \begin{sideways}Rust\end{sideways}
        \\
        \hline
        \endhead
        \hline \multicolumn{11}{r}{\textit{Continued on next page}} \\
        \endfoot
        \hline
        \endlastfoot
        String \textbf{capitalize} & No &  &  &  &  & &  &  & 1 & 1 \\

        Get \textbf{char-at} a given position & Yes &  &  &  &  & &  &  & 1 & 1 \\

        Strings \textbf{compare} & Yes &  &  &  &  & &  &  & n & n \\

@@

        Strings \textbf{concatenate} & Yes &  &  &  &  & &  &  & n & n \\

        Check if \textbf{containts} substring & Yes &  &  &  &  & &  &  & n & n \\

        \textbf{count} of substring in string & No &  &  &  &  & &  &  &  & \\

        Check if \textbf{ends-with} a substring & Yes &  &  &  &  & &  &  & n & n \\

        Check if \textbf{equals} & Yes &  &  &  &  & &  &  & n & n \\

        \textbf{find-first} substring in string & Yes &  &  &  &  & &  &  & n & n \\

        \textbf{find-last} substring in string & Yes &  &  &  &  & &  &  & n & n \\

        \textbf{format} string by regexp & Yes &  &  &  &  & &  &  & n & n \\

        Get string \textbf{hash} & Yes &  &  &  &  & &  &  & n & n \\

        \textbf{insert} in string by index & No &  &  &  &  & &  &  & n & n \\

        Check if \textbf{is-alphabetic} & No &  &  &  &  & &  &  & n & n \\

        Check if \textbf{is-empty} & Yes &  &  &  &  & &  &  & 1 & 1 \\

        Check if \textbf{is-hexadecimal} & No &  &  &  &  & &  &  & n & n \\

        Check if \textbf{is-int} & No &  &  &  &  & &  &  & n & n \\

        Check if \textbf{is-lowercase} & No &  &  &  &  & &  &  & n & n \\

        Check if \textbf{is-uppercase} & No &  &  &  &  & &  &  & n & n \\

        Check if \textbf{is-whitespace} & No &  &  &  &  & &  &  & n & n \\

        \textbf{join} list of strings & No &  &  &  &  & &  &  & n & n \\

        Get string \textbf{length} & Yes &  &  &  &  & &  &  & 1 & 1 \\

        Check if string \textbf{matches-regexp} & Yes &  &  &  &  & &  &  & n & n \\

        Get string \textbf{partition} & No &  &  &  &  & &  &  & n & n \\

        \textbf{repeat} string number of times & No &  &  &  &  & &  &  & n & n \\

        \textbf{replace-all} substrings by other & Yes &  &  &  &  & &  &  & n & n \\

        \textbf{replace-first} substrings by other & Yes &  &  &  &  &  &  &  &  & \\

        String \textbf{split} & Yes &  &  &  &  & &  &  & n & n \\

        Check if \textbf{starts-with} a substring & Yes &  &  &  &  & &  &  & n & n \\

        String \textbf{strip} & Yes &  &  &  &  & &  &  & n & n \\

        Get \textbf{substring} by positions & Yes &  &  &  &  & &  &  & n & 1 \\

        String \textbf{swap-case} & No &  &  &  &  & &  &  & n & n \\

        String \textbf{to-float} & No &  &  &  &  & &  &  & n & n \\

        String \textbf{to-int} & No &  &  &  &  & &  &  & n & n \\

        String \textbf{to-lowercase} & Yes &  &  &  &  & &  &  & n & n \\

        String \textbf{to-uppercase} & Yes &  &  &  &  & &  &  & n & n \\

        String \textbf{trim-left} & No &  &  &  &  &  &  &  & n & n \\

        String \textbf{trim-right} & No &  &  &  &  & &  &  & n & n \\

        \textbf{remove} substring by positions & No &  &  &  &  & &  &  &  & \\

        String \textbf{uncapitalize} & No &  &  &  &  & &  &  &  & \\

        Get string \textbf{as-bytes} & Yes &  &  &  &  & &  &  &  & \\

        String \textbf{pop-back} & No &  &  &  &  & &  &  &  & \\

        Get string \textbf{as-chars} & Yes &  &  &  &  & &  &  &  & \\

        Get string \textbf{as-canonical} & Yes &  &  &  &  & &  &  &  & \\

        Check if \textbf{is-ascii} & No &  &  &  &  & &  &  &  & \\

        String \textbf{copy} & Yes &  &  &  &  & &  &  &  & \\

        String \textbf{contains-any} & No &  &  &  &  & &  &  &  & \\

        String \textbf{reserve-capacity} & No &  &  &  &  & &  &  &  & \\

        String \textbf{shrink-to-fit} & No &  &  &  &  & &  &  &  & \\ \hline
        \caption{String functions existing in languages}
        \label{tab:my_label}
    \end{longtable}

>>>>

    \begin{longtable}{lllllllllll}
        \hline
        & \begin{sideways}Java\end{sideways}
        & \begin{sideways}Ruby\end{sideways}
        & \begin{sideways}Python\end{sideways}
        & \begin{sideways}C++\end{sideways}
        & \begin{sideways}JavaScript\end{sideways}
        & \begin{sideways}Go\end{sideways}
        & \begin{sideways}C\#\end{sideways}
        & \begin{sideways}Swift\end{sideways}
        & \begin{sideways}PHP\end{sideways}
        & \begin{sideways}Rust\end{sideways}
        \\
        \hline
        \endfirsthead
        \multicolumn{11}{c}%
        {\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
        \hline
        & \begin{sideways}Java\end{sideways}
        & \begin{sideways}Ruby\end{sideways}
        & \begin{sideways}Python\end{sideways}
        & \begin{sideways}C++\end{sideways}
        & \begin{sideways}JavaScript\end{sideways}
        & \begin{sideways}Go\end{sideways}
        & \begin{sideways}C\#\end{sideways}
        & \begin{sideways}Swift\end{sideways}
        & \begin{sideways}PHP\end{sideways}
        & \begin{sideways}Rust\end{sideways}
        \\
        \hline
        \endhead
        \hline \multicolumn{11}{r}{\textit{Continued on next page}} \\
        \endfoot
        \hline
        \endlastfoot
        String \textbf{capitalize} & No & Yes &  &  &  & &  &  & 1 & 1 \\

        Get \textbf{char-at} a given position & Yes & Yes &  &  &  & &  &  & 1 & 1 \\

        Strings \textbf{compare} & Yes & No &  &  &  & &  &  & n & n \\

@@

        Strings \textbf{concatenate} & Yes & No &  &  &  & &  &  & n & n \\

        Check if \textbf{contains} substring & Yes & No &  &  &  & &  &  & n & n \\

        \textbf{count} of substring in string & No & Yes &  &  &  & &  &  &  & \\

        Check if \textbf{ends-with} a substring & Yes & Yes &  &  &  & &  &  & n & n \\

        Check if \textbf{equals} & Yes & No &  &  &  & &  &  & n & n \\

        \textbf{find-first} substring in string & Yes & Yes &  &  &  & &  &  & n & n \\

        \textbf{find-last} substring in string & Yes & No &  &  &  & &  &  & n & n \\

        \textbf{format} string by regexp & Yes & Yes &  &  &  & &  &  & n & n \\

        Get string \textbf{hash} & Yes & No &  &  &  & &  &  & n & n \\

        \textbf{insert} in string by index & No & No &  &  &  & &  &  & n & n \\

        Check if \textbf{is-alphabetic} & No & Yes &  &  &  & &  &  & n & n \\

        Check if \textbf{is-empty} & Yes & Yes &  &  &  & &  &  & 1 & 1 \\

        Check if \textbf{is-hexadecimal} & No & No &  &  &  & &  &  & n & n \\

        Check if \textbf{is-int} & No & Yes &  &  &  & &  &  & n & n \\

        Check if \textbf{is-lowercase} & No & Yes &  &  &  & &  &  & n & n \\

        Check if \textbf{is-uppercase} & No & Yes &  &  &  & &  &  & n & n \\

        Check if \textbf{is-whitespace} & No & Yes &  &  &  & &  &  & n & n \\

        \textbf{join} list of strings & No & Yes &  &  &  & &  &  & n & n \\

        Get string \textbf{length} & Yes & No &  &  &  & &  &  & 1 & 1 \\

        Check if string \textbf{matches-regexp} & Yes & No &  &  &  & &  &  & n & n \\

        Get string \textbf{partition} & No & Yes &  &  &  & &  &  & n & n \\

        \textbf{repeat} string number of times & No & No &  &  &  & &  &  & n & n \\

        \textbf{replace-all} substrings by other & Yes & Yes &  &  &  & &  &  & n & n \\

        \textbf{replace-first} substrings by other & Yes & Yes &  &  &  &  &  &  &  & \\

        String \textbf{split} & Yes & Yes &  &  &  & &  &  & n & n \\

        Check if \textbf{starts-with} a substring & Yes & Yes &  &  &  & &  &  & n & n \\

        String \textbf{strip} & Yes & Yes &  &  &  & &  &  & n & n \\

        Get \textbf{substring} by positions & Yes & No &  &  &  & &  &  & n & 1 \\

        String \textbf{swap-case} & No & Yes &  &  &  & &  &  & n & n \\

        String \textbf{to-float} & No & No &  &  &  & &  &  & n & n \\

        String \textbf{to-int} & No & No &  &  &  & &  &  & n & n \\

        String \textbf{to-lowercase} & Yes & Yes &  &  &  & &  &  & n & n \\

        String \textbf{to-uppercase} & Yes & Yes &  &  &  & &  &  & n & n \\

        String \textbf{trim-left} & No & Yes &  &  &  &  &  &  & n & n \\

        String \textbf{trim-right} & No & Yes &  &  &  & &  &  & n & n \\

        \textbf{remove} substring by positions & No & No &  &  &  & &  &  &  & \\

        String \textbf{uncapitalize} & No & No &  &  &  & &  &  &  & \\

        Get string \textbf{as-bytes} & Yes & No &  &  &  & &  &  &  & \\

        String \textbf{pop-back} & No & No &  &  &  & &  &  &  & \\

        Get string \textbf{as-chars} & Yes & No &  &  &  & &  &  &  & \\

        Get string \textbf{as-canonical} & Yes & No &  &  &  & &  &  &  & \\

        Check if \textbf{is-ascii} & No & Yes &  &  &  & &  &  &  & \\

        String \textbf{copy} & Yes & No &  &  &  & &  &  &  & \\

        String \textbf{contains-any} & No & No &  &  &  & &  &  &  & \\

        String \textbf{reserve-capacity} & No & No &  &  &  & &  &  &  & \\

        String \textbf{shrink-to-fit} & No & No &  &  &  & &  &  &  & \\ \hline
        \caption{String functions existing in languages}
        \label{tab:my_label}
    \end{longtable}
